### 2009-11-04 doc/manuals/user_interface/ui-data.tex
CLI manual: moved chelonia section under doc/chelonia, fixed Makefile
bring up to date arc data client examples

\subsection{arcls}\label{sec:arcls}
The \texttt{arcls} \index{arcls}\index{commands:arcls} is a simple
utility that allows to list contents and view some attributes of
objects of a specified (by an URL) remote directory.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded and\\ & & temporary cached locations\\
    \texttt{-m} && display all available metadata\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

@@

\begin{verbatim}
    arcls rls://rc.host:38203/logical_file_name
    arcls -l gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535
    arcls -L srm://grid.uio.no:58000/srm/managerv1/johndoe/log2
\end{verbatim}

@@

The \texttt{arccp} \index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

@@

\begin{verbatim}
    arccp gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535/job.out \
              file:///home/myname/job2.out
    arccp gsiftp://aftpexp.bnl.gov;threads=10/rep/my.file \
              rc://;threads=4@grid.uio.no/lc=Collection,rc=Catalog/zebra4.f
    arccp http://www.nordugrid.org/data/somefile gsiftp://hathi.hep.lu.se/data/
\end{verbatim}

@@

The \texttt{arcrm} \index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{arcrm} is to erase the files in a data
   indexing catalog (RC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

@@

\begin{verbatim}
    arcrm rc://grid.uio.no/lc=Collection,rc=Catalog/badfile
\end{verbatim}

@@

ACL document (an XML file) is printed to standard output when
\texttt{get} is requested, and is acquired from standard input when
\texttt{set} is specified\footnote{In ARC $\leq$ 0.5.28, \texttt{set}
  shoud be used instead of \texttt{put}}. Usage examples are:
\begin{verbatim}
    arcacl get gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename
    arcacl set gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename $<$ myacl
\end{verbatim}

\subsection{arctransfer}\label{sec:arctransfer}
\index{arctransfer}\index{commands:arctransfer}The \texttt{arctransfer}
This command is not implemented.

>>>>

\subsection{arcls}\label{sec:arcls}
\texttt{arcls}\index{arcls}\index{commands:arcls} is a simple
utility that allows to list contents and view some attributes of
objects of a specified (by a URL) remote directory.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcls [options] $<$URL$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-l} &  & detailed listing\\
    \texttt{-L} &  & detailed listing including URLs from which file can 
    be downloaded\\
    \texttt{-m} && display all available metadata\\
    Arguments:&&\\
    \texttt{URL} && file or directory URL\\
\end{longtable}

@@

\begin{verbatim}
    arcls -L rls://rls.nordugrid.org:38203/logical_file_name
    arcls -l gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535
    arcls srm://grid.uio.no:8446/srm/managerv2?SFN=/johndoe/log2
\end{verbatim}

@@

\texttt{arccp}\index{arccp}\index{commands:arccp} is a powerful
tool to copy files over the Grid. It is a part of the A-REX,
but can be used by the User Interface as well.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccp [options] $<$source$>$ $<$destination$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-y} & \textit{cache\_path} & path to local cache (use to put file into cache)\\
    \texttt{-p} && use passive transfer (does not work if secure is on, default if secure is not requested)\\
    \texttt{-n} && do not try to force passive transfer\\
    \texttt{-i} && show progress indicator\\
    \texttt{-u} && use secure transfer (insecure by default)\\
    \texttt{-r} & \textit{recursion\_level} & operate recursively (if possible) up to specified level (0 - no recursion)\\
    \texttt{-R} & \textit{number} & how many times to retry transfer of every file before failing\\
    \texttt{-t} & \textit{time} & timeout in seconds (default 20)\\
    \texttt{-f} && if the destination is an indexing service and not the same as the source and the destination is already registered, then the copy is normally not done. However, if this option is specified the source is assumed to be a replica of the destination created in an uncontrolled way and the copy is done like in case of replication\\
    \texttt{-T} && do not transfer file, just register it - destination must be non-existing meta-url\\
    Arguments:&&\\
    \texttt{source} && source URL\\
    \texttt{destination} && destination URL\\
\end{longtable}

@@

\begin{verbatim}
    arccp gsiftp://lscf.nbi.dk:2811/jobs/1323842831451666535/job.out \
              file:///home/myname/job2.out
    arccp gsiftp://aftpexp.bnl.gov;threads=10/rep/my.file \
              rls://grid.uio.no/zebra4.f
    arccp http://www.nordugrid.org/data/somefile gsiftp://hathi.hep.lu.se/data/
\end{verbatim}

@@

The \texttt{arcrm}\index{arcrm}\index{commands:arcrm}
command allows users to erase files at any location specified by a
valid URL.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcrm [options] $<$source$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
    \texttt{-h} && short help\\
    \texttt{-v} && print version information\\
    \texttt{-d} & \textit{debuglevel} &debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
    \texttt{-c} & &continue with meta-data even if it failed to delete real file\\
    Arguments:&&\\
    \texttt{source} && source URL\\
\end{longtable}

\begin{framed}
   A convenient use for \texttt{arcrm} is to erase the files in a data
   indexing catalog (LFC, RLS or such), as it will not only remove the
   physical instance, but also will clean up the database record.
\end{framed}

@@

\begin{verbatim}
    arcrm lfc://grid.uio.no/grid/atlas/AOD_0947.pool.root
\end{verbatim}

@@

The ACL document (an XML file) is printed to standard output when
\texttt{get} is requested, and is acquired from standard input when
\texttt{set} is specified\footnote{In ARC $\leq$ 0.5.28, \texttt{set}
  was used instead of \texttt{put}}. Usage examples are:
\begin{verbatim}
    arcacl get gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename
    arcacl set gsiftp://se1.ndgf.csc.fi/ndgf/tutorial/dirname/filename < myacl
\end{verbatim}

\subsection{arctransfer}\label{sec:arctransfer}
\index{arctransfer}\index{commands:arctransfer}
The \texttt{arctransfer} command is not implemented.
